\TITLE

### 2010-06-08 devel_path/plfs_roadmap.tex
git-svn-id: https://plfs.svn.sourceforge.net/svnroot/plfs/doc@164 979fb63a-54b4-4514-8d67-9ab8ea1b59df

>>>>

OK.  Here the current plan:

\begin{itemize}
\item{global mkdir for logical directories}
\item{local mkdir for container directories hashed by node name}
\item{local create for files hashed by node name}
\item{global parallel metadata ops (including things like chmod)}
\end{itemize}

The global parallel metadata ops do leave us vulnerable to crashes.  We
need a new term to explain this.  With striping across volumes, on an
N-1 write workload, we'll have multiple nodes each create
"subcontainers" on different volumes.  Each subcontainer will be created
in exactly the same way that containers are created now.  On a read,
PLFS will aggregate the indices from all the subcontainers and construct
a global view of the container.  So the consistency problem is that we
crash halfway through a chmod.  Each subcontainer will have an
accessfile that holds its permissions.  When we go to aggregate the
subcontainers' permissions into the permissions for the container, we'll
discover that they are not consistent.  I guess in this specific case,
we'll just use the strictest.  If the user is surprised, they'll just do
a chmod again to fix it.  I'll have to think whether worse problems
occur for other possible inconsistencies.

\definition{Subcontainer}{If multiple nodes each create containers for
the same logical file on different volumes, each of these is actually
a \Term{subcontainer} and the logical aggregated view is a \Term{container}.
To aggregate a view of a container, \plfs\ will look across all {\store}s
for subcontainers for that container.}

By the way, we used to use the link idea back before I stripped the
volume striping out.  This work by hashing the container itself by name
and the hostdirs within were hashed by node and then lazily linked in to
the container.  You could do the link at create time but then there is a
parallel open storm.  This avoided the consistency problem and made
lookups easier.  It also meant that the read worked for free.  In the
above approach, we might have to modify the global index build since the
data droppings are striped across multiple directories.  But I didn't
like that approach since lazily linking in the hostdirs was complicated.
